Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-27 paper.tex
more of modularity

            LONI and FastR are other examples of workflow engines that use an
            XML interface to describe CLIs. LONI enables generation of the 
            XML-based module interface through its GUI. The module interface
            consists of details on \note{from website} module metadata (e.g.
            authors, package, version, name) and citation information, 
            command-line syntax, parameter and file types, dependencies and 
            output and error handling.

@@

            Some workflows do not require module interfaces, as is the case with
            Make.

>>>>

            LONI, FastR, Taverna and Pegasus are other examples of workflow 
            engines that 
            use an XML interface to describe CLIs. LONI enables generation of 
            the XML-based module interface through its GUI. The module interface
            consists of details on \note{from website} module metadata (e.g.
            authors, package, version, name) and citation information, 
            command-line syntax, parameter and file types, dependencies and 
            output and error handling.

@@

            Tool addition in Taverna is primarily performed through the user 
            interface, but can also achieved through the creation of an XML
            descriptor. Taverna differs from other workflow engines in that it
            execute generic-style services (i.e. WSDL and REST) in addition to
            other types of Web Services, as well a external CLIs, R scripts and
            Java services. To interface with a CLI, the XML file must contain 
            the command to execute, file inputs and outputs (if required), if 
            standard input, output and error streams must be conserved and the 
            location where the command should execute\note{from website}.

            Pegasus is another workflow engine that uses an XML format to 
            define the CLI tools interface. The XML interfaces are typically 
            incorporated directly into the workflow DAX definition. However, a 
            separate multiline text-based 'Transformation Catalogue' file can
            be provided. Information encoded within the interfaces include
            tool identifier (typically namespace::version), the URL or filepath
            to the executable, site identifier of the executable's host, 
            executable type (e.g. installed or staged) and the profile. Pegasus
            can also execute containerized tools. For this, a container 
            identifier, image URL, site identifier of the image, and container
            profiles must also be defined.

            Some workflows do not require module interfaces, as is the case with
            Make. The pipeline is expressed in a makefile containing a set of 
            rules. Rules consist of three components: targets, dependencies and
            recipes. The target is the output (typically a file) of the 
            execution of a recipe and the dependencies are the input required to 
            produce the given target. Recipes are the shell commands that will
            generate the target from its dependencies. As makefiles are written
            entirely using shell commands, it is not necessarily to create 
            interfaces to the shell commands of the tools.
